\documentclass[10pt,a4paper,ragged2e]{altacv}

\geometry{left=1.5cm,right=1.5cm,top=2cm,bottom=2cm}

\usepackage[default]{lato}
\usepackage{graphicx}
\usepackage{fontawesome5}
\usepackage{xcolor} % Ensure color package is included

% Define the colors
\definecolor{VividPurple}{HTML}{3E0097}
% \definecolor{SlateGrey}{HTML}{708090}
% \definecolor{LightGrey}{HTML}{D3D3D3}
\colorlet{heading}{VividPurple}
% \colorlet{emphasis}{SlateGrey}
% \colorlet{body}{LightGrey}

\begin{document}

\cvsection{Cover Letter}


\vspace{1em} % Space before the greeting

Dear Air New Zealand Recruitment Team,

\vspace{1em} % Space before the body

I am writing to express my enthusiasm for the Principal AI Infrastructure Engineer (Principle Data Science and Engineering Specialist) position at Air New Zealand, as advertised. With a deep-seated passion for artificial intelligence and over 10 years of experience in Data Engineering and Architecture, I am excited about the opportunity to contribute to your mission of becoming the world's best Digital Airline.

\vspace{1em}

At my current role in IDEXX LABORATORIES, I have partaken in the design and implementation of AI solutions that led to significantly positive feedbacks from our customers. My hands-on experience with cloud platforms, coupled with my proficiency in multi-cloud environments and tools like Terraform and Ansible, aligns perfectly with the requirements of this role. I have led teams in deploying innovative data and AI infrastructures that have propelled companies forward in their digital transformation journeys. In addition, I have been doing a PhD in computer science focusing on decentralised and distributed big data architectures, the details of which can be found on my resume. 

\vspace{1em}

Your emphasis on leveraging AI to drive exciting change resonates with me. I am particularly drawn to Air New Zealand's forward-thinking approach and its commitment to using AI for innovation. My experience in designing robust AI infrastructures and deploying AI initiatives positions me as an ideal candidate for Air New Zealand's data science and engineering projects. Furthermore, my curiosity and ability to navigate complex problems in data that is sometimes incomplete or inaccurate have been pivotal in my previous roles.

\vspace{1em}

I am eager to bring my blend of expertise in AI platform technology stacks, including Vector Databases and LangChain, to Air New Zealand. The prospect of working within a team that values collaboration, innovation, and flexibility excites me, and I am motivated by the challenge of contributing to your vision.

\vspace{1em}

Thank you for considering my application. I am keen on the opportunity to discuss how my background, skills, and enthusiasms align with the needs of Air New Zealand. I am looking forward to potentially contributing to your team and playing a part in Air New Zealand's journey towards becoming a global leader in digital aviation.

\vspace{1em}

Sincerely,


\vspace{2em} % Space before your name

Sincerely, \newline
Pouya Ataei.

\end{document}
