\documentclass[10pt,a4paper,ragged2e]{altacv}

\geometry{left=1.5cm,right=1.5cm,top=2cm,bottom=2cm}

\usepackage[default]{lato}
\usepackage{graphicx}
\usepackage{fontawesome5}
\usepackage{xcolor} % Ensure color package is included
\usepackage{parskip}

% Define the colors
\definecolor{VividPurple}{HTML}{3E0097}
% \definecolor{SlateGrey}{HTML}{708090}
% \definecolor{LightGrey}{HTML}{D3D3D3}
\colorlet{heading}{VividPurple}
% \colorlet{emphasis}{SlateGrey}
% \colorlet{body}{LightGrey}

\begin{document}

\cvsection{Cover Letter}


\vspace{1em} % Space before the greeting

Dear Hiring Manager,

It is with great enthusiasm that I submit my application for the Technical Lead position within the Digital Products team at Les Mills International. As a seasoned software engineer and computer scientist with over a decade of experience in developing robust, efficient, and scalable solutions, I am confident in my ability to drive technical delivery and manage vendors while contributing to your mission of creating a fitter planet.

Throughout my career, I have held positions of increasing responsibility, including Software Engineer, Tech Lead, Lead Architect, Development Leader, Researcher, and Teacher. My passion for perceiving the complexities within simplicities and viewing challenges through the prism of creativity has been a driving force behind my success in delivering high-quality software solutions.

As a Lead Development Architect at Idexx Laboratories, I have been instrumental in making critical technological decisions across different regions, introducing event-driven architectures, and designing infrastructure, applications, and integrations on a daily basis. My experience in coaching and mentoring junior, intermediate, and senior engineers, as well as applying servant leadership principles, has fostered a culture of trust, collaboration, and continuous learning within my teams.

My technical expertise spans a wide array of technologies, including JavaScript/TypeScript, React, Redux, Node, Golang, Rust, C/C++, AWS, Google Cloud, Azure, Kubernetes, and more. I have a strong foundation in software architecture, distributed systems, design patterns, data structures, and algorithms, which allows me to tackle complex challenges and deliver innovative solutions.

Beyond my technical skills, I have a proven track record of engaging with stakeholders, presenting at conferences, and contributing to the academic community through publications and presentations. My ability to effectively communicate complex technical concepts and collaborate with cross-functional teams has been instrumental in driving successful project outcomes.

I am particularly drawn to Les Mills International's commitment to creating a flexible, diverse, and inclusive environment. As someone who values work-life balance and the opportunity to make a positive impact on a global scale, I am excited about the prospect of joining your team and contributing to your steep growth goals and industry-leading innovations.

Thank you for considering my application. I look forward to the opportunity to further discuss how my skills, experience, and passion for technology can contribute to the success of the Digital Products team at Les Mills International.


\vspace{2em} % Space before your name

Sincerely, \newline
Pouya Ataei.

\end{document}
