\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\begin{document}

\begin{flushright}
Pouya Ataei\\
pouya.ataei.7@gmail.com\\
\href{https://www.linkedin.com/in/pouya-ataei-bb1254ba}{LinkedIn Profile}\\
\today
\end{flushright}

\begin{flushleft}
Databricks Hiring Team\\
Engineering Department
\end{flushleft}

Dear Databricks Hiring Team,

\vspace{1em}

As a data enthusiast with a PhD in Big Data and over a decade of experience in software engineering, I am excited to apply for the Senior Staff Software Engineer position at Databricks. My passion for data runs so deep that I dedicated years to researching big data systems, culminating in my doctoral thesis on optimizing distributed data processing frameworks.

Your vision of the Lakehouse and the challenge of outperforming specialized SQL query engines while supporting diverse workloads resonates strongly with my research focus and professional experience. At Invenco by GVR, I led a team that scaled our payment terminal infrastructure to handle over 300,000 requests in under 30 minutes, demonstrating my ability to architect and implement high-performance, fault-tolerant systems at scale.

My experience aligns closely with your requirements:

\begin{itemize}
    \item 15+ years of industry experience, including leadership roles in cloud services and distributed systems
    \item Proven track record of delivering customer value, as evidenced by my work on observability plans using OpenTelemetry at Invenco
    \item Strong foundation in algorithms and data structures, honed through my academic research and practical application in industry
    \item Experience driving initiatives towards customer satisfaction, including collaborating with stakeholders to define technical roadmaps
    \item PhD in Computer Science with a focus on Big Data systems
\end{itemize}

I'm particularly drawn to Databricks' commitment to solving real-world problems through data and AI. My research on optimizing data processing pipelines for cancer genomics aligns with your mission of enabling data teams to tackle crucial challenges like cancer drug development.

The opportunity to join as a founding member of the Berlin site and contribute to the multi-year Lakehouse vision is incredibly exciting. I'm prepared to leverage my expertise in distributed systems, performance optimization, and team leadership to drive Databricks' innovation forward.

I look forward to the possibility of discussing how my passion for data, technical expertise, and leadership experience can contribute to Databricks' mission of empowering data teams worldwide.

\vspace{1em}

Sincerely,

\vspace{2em}

Pouya Ataei

\end{document}
